### 2021-07-05 docs/manuscript/manuscript.tex
Rephrase introduction

Producing a stripe of gene expression is a fundamental patterning function
in development, and it has been shown that feed-forward motifs are minimal
networks capable of performing this function~\cite{munteanu_2014}. For example,
Cotterell and Sharpe studied what kind of 3-node network topologies could
interact with a morphogen gradient and produce a stripe of gene expression
in a one-dimensional field of cells and found a variety of networks that
implemented at least 7 different mechanisms and had different levels of
complexity, being most of them variations of feed-forward motifs~\cite{Cotterell2010}.

However, although several studies have analyzed the properties of GRNs that
process positional information, they have focused on particular natural
networks~\cite{Schaerli2014,Jaeger2004}, in synthetic networks~\cite{Basu2005,
Reinitz1995,Schaerli2018,Elowitz2000}, or have constrained the
design of the GRNs to accept an input signal from only one of its nodes, which is
not always biologically realistic as multiple input systems can exist~\cite{Cotterell2010,
munteanu_2014, Schaerli2014}. For example, the neural subtypes specification
system in the vertebrate neural tube is a two-input network in which
Sonic Hedgehog acts as a morphogen and Olig2 and Nkx2.2 act as the receiver
nodes~\cite{dessaud_dynamic_2010, balaskas2012, exelby_2021}.

>>>>

In a tissue context, the generation of a stripe of gene expression is a fundamental
patterning function in development, and it has been shown that simple feed-forward
motifs can robustly achieve such a patterning task~\cite{munteanu_2014}. For
example, Cotterell and Sharpe studied  what kind of 3-node network topologies
could effectively translate a morphogen gradient into a striped gene expression
pattern in a one-dimensional field of cells, and found a variety of networks that
implemented at least 7 different mechanisms with varying levels of complexity,
being most of them variations of feed-forward motifs~\cite{Cotterell2010}.

Although GRNs with positional information processing capacities have been
extensively analyzed, most studies have so far placed emphasis on particular
regulatory systems that respond to a single input only. These studies have
typically focused on either regulatory systems observed in
nature~\cite{vonDassow2000,Reinitz1995,Jaeger2004}, synthetic
implementations~\cite{Basu2005,Schaerli2018,Elowitz2000,barbier2020} with
predefined topologies, or have deliberately constrained the study of GRNs to just
a handful of alternative designs~\cite{munteanu_2014,Schaerli2014}. However,
previous work has demonstrated the necessity to expand computational analysis
of pattern forming GRNs to multi-input settings. For instance, it has been shown
that the neural subtypes specification system in the vertebrate neural tube involves
a  two-input network in which Sonic Hedgehog acts as a morphogen and the Olig2
and Nkx2.2 genes can act as the receiver nodes~\cite{dessaud_dynamic_2010,
balaskas2012, exelby_2021}.
